Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-10-30 paper/main.tex
add structure

\manuel{}{
  \begin{itemize}
  \item Who else has used Mallows model for black-box optimization? Ekhine: Va a mirarlo.
  \item Who else has used unbalanced borda for optimization? Ekhine va a añadir 2 frases.
  \end{itemize}
}
This paper structured as follows \MANUEL{Mío}

@@

\section{Unbalanced Mallows model (UMM)}

@@

\section{Experimental setup}

@@

\section{Experimental analysis}

@@

\section{Conclusions}

>>>>

\manuel{}{
  \begin{itemize}
  \item Who else has used Mallows model for black-box optimization? Ekhine: Va a mirarlo.
  \item Who else has used unbalanced borda for optimization? Ekhine va a añadir 2 frases.
  \end{itemize}
}
This paper structured as follows. Section~\ref{sec:backgroud} summarizes fundamental concepts about permutation spaces, the uBorda algorithm, black-box combinatorial optimization under a limited budget and CEGO, a Bayesian optimizer for such problems. Section~\ref{sec:umm} presents the UMM algorithm, which is the main contribution of this paper. UMMA is analyzed using the experimental setup presented in Section~\ref{sec:setup} and results are presented in Section~\ref{sec:analysis}. We end the paper with overall conclusions and a call for further research on this type of optimization scenario (Section~\ref{sec:conclusions}).

@@

\section{Unbalanced Mallows model (UMM)}\label{sec:umm}

@@

\section{Experimental setup}\label{sec:setup}

@@

\section{Experimental analysis}\label{sec:analysis}

@@

\section{Conclusions}\label{sec:conclusions}
